---
title: "Introduction to GSO"
author: "Contamin Lucie"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

GSO is the General Statistics Office of Vietnam ([GSO](http://gso.gov.vn/Default_en.aspx?tabid=491)).  The `gso` package contains the updated (last update 03/2017), cleaned and tidy version of all the 316 tables available on the website. For the moment, only 113 data frames and 1 summary data frame are available within this package (more details in this vignette).

Installing the `gso` package:

```{r, eval=F}
devtools::install_github("choisy/gso")
```

Loading and attaching the `gso` package:

```{r}
library(gso)
```

## Content data frame

The package contains a data frame called `content` containing for each row, a data frame (in the column `data`) and some description of this data frame:

```{r}
head(content)
```

The data frame contains different columns describing the data: 

* `category` : global theme of the data frame. 
* `subcategory` : subcategory of the data frame
* `time_range` : time range expressed in year
* `time_resolution` : unit of time used in the data frame (year, month or single time point)
* `sp_resoluation` : spatial unit used in the data frame (province, stations, city, rivers ...)
* `data_frame` : name of the data frames on gso
* `data_name` : name of the data frames in the package

For more details:
```{r eval=F}
?content
```

You can used `content` to select the data frame necessary for your study.
You can filter the data by the category, subcategory or others parameters to see the data available by different criterium:

```{r}
agri_forest_fish <- subset(content, category == "Agriculture, Forestry and Fishery", data)
agri_forest_fish <- agri_forest_fish$data[[1]]
str(agri_forest_fish)
```

or, to select a data frame related to HIV in Vietnam

```{r}
sel <- grep("hiv", content$data_frame, ignore.case = TRUE)
content[sel, ] # permit to print more information
df_hiv <- content[sel, "data"]
df_hiv <- df_hiv$data[[1]]
head(df_hiv)
```

Or you can also used the function `View()` to print the data frame and explore all the data available, but the display can be quite long to open because of the column `data`

```{r, eval = F}
View(content)
```
